Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-10-03 Phase_II/draft/II.tex
the first

Intensity Interferometry counts the photons arriving at the telescopes from the stellar object. The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}. The left panel of fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on linear scales. Point to note here is that this figure represents the signal from the source that would be recorded by an infinite number of baselines provided by an infinite number of telescopes on the interferometric plane. In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule. We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night. Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
\begin{figure*}
   \centering
  \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
  \caption{This merged image shows the input for GAN. The left figure is the simulated source, which act as a ground truth for GAN while training the model. The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}), which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained. The grey scale of the figure is normalized to the brightest pixel in the image.}
  \label{fig:GANinput}
\end{figure*}

>>>>

Intensity Interferometry counts the photons arriving at the telescopes from the stellar object. The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}. The left panel of fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on linear scales. Point to note here is that this figure represents the signal from the source that would be recorded by an infinite number of baselines provided by an infinite number of telescopes on the interferometric plane. In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule. We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night. Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
\begin{figure*}
   \centering
  \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
  \caption{This merged image shows the input for GAN. The left figure is the simulated source, which act as a ground truth for GAN while training the model. The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}) with salt and paper noise, which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained. The grey scale of the figure is normalized to the brightest pixel in the image.}
  \label{fig:GANinput}
\end{figure*}

### 2025-10-03 Phase_II/draft/ParaGan.tex
the first

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{fig/testing_image/image_1.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_4.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_10.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (right panel of of fig.\ref{fig:ft}). This image is presented, as the input, to the trained GAN to produce a predicted image. The second panel is the real image of the star, also called the ground truth. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane. The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane. }
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II. Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.

>>>>

\section{Network Parameters}
\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{fig/testing_image/image_7.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_13.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_29.png}
	\includegraphics[width=\linewidth]{fig/testing_image/image_39.png}
\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work. Each row in this figure represents the results for a hypothetical fast-rotating star. Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (right panel of of fig.\ref{fig:ft}). This image is presented, as the input, to the trained GAN to produce a predicted image. The second panel is the real image of the star, also called the ground truth. The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model . The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane. The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane. }
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II. Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
